Text Is All You Need

### 2023-05-05 docs/hes_final/article.qmd
tweak letter caps
Title Tweak and Emails

---
title: Text Is All You Need
subtitle: Predicting conflict escalation with news article text content
author:
  - name: Diana Kolusheva
    email: email@h
    affiliation: Harvard University
  - name: Chad Stoughton
    email: email@h
    affiliation: Harvard University
  - name: Evan Wheeler
    email: evw217@g.harvard.edu
    affiliation: Harvard University
lang: en
format:
  pdf:
    documentclass: scrartcl
    classoption:
    - twocolumn
    margin-left: 25mm
    margin-right: 25mm
    margin-top: 25mm
    margin-bottom: 25mm
    whitespace: medium
    mermaid:
      theme: neutral
    keep-tex: true
bibliography: bibliography.bibtex
# https://stackoverflow.com/a/75043433
template-partials: 
- title.tex
# https://github.com/quarto-dev/quarto-cli/discussions/2786
include-in-header:
  - text: |
      \usepackage[noblocks]{authblk}
      \renewcommand*{\Authsep}{, }
      \renewcommand*{\Authand}{, }
      \renewcommand*{\Authands}{, }
      \renewcommand\Affilfont{\small}
      \usepackage{float}
      \makeatletter
      \let\oldlt\longtable
      \let\endoldlt\endlongtable
      \def\longtable{\@ifnextchar[\longtable@i \longtable@ii}
      \def\longtable@i[#1]{\begin{figure}[H]
      \onecolumn
      \begin{minipage}{0.5\textwidth}
      \oldlt[#1]
      }
      \def\longtable@ii{\begin{figure}[H]
      \onecolumn
      \begin{minipage}{0.5\textwidth}
      \oldlt
      }
      \def\endlongtable{\endoldlt
      \end{minipage}
      \twocolumn
      \end{figure}}
      \makeatother
       \usepackage[font=small,labelfont={bf,small}]{caption}
# https://tex.stackexchange.com/questions/31301/how-to-reduce-the-number-of-hyphenation
include-before-body:
  - text: |
      \pretolerance=5000
      \tolerance=9000
      \emergencystretch=0pt
      \exhyphenpenalty=100
      \righthyphenmin=4
      \lefthyphenmin=5
      \setlength{\belowcaptionskip}{-5pt}
embed-resources: true
notebook-links: false
title-block-banner: true
abstract: |
  The task of forecasting conflict escalation is of great interest to policy makers, executives, and social scientists. In this article, we propose a novel, text-first approach to computational conflict prediction using contemporary natural language processing and machine learning techniques. We outline three methods to extract generalizable conflict signals directly from a corpus of over 2.5 million document embeddings derived from publicly available news sources. The first uses text data enriched by country context features, the second uses text data conditioned only on the country label itself, and the third extracts a signal from the text alone, with no additional country or region-specific features. We demonstrate that signals suggesting impending conflict can be extracted directly from text sources, and we outline potential avenues for further research that we believe may yield models that can provide early warnings to decision makers to facilitate strategic planning, resource allocation, and disaster mitigation.

>>>>

---
title: Text Is All You Need
subtitle: Predicting Conflict Escalation Using Global News Content
author:
  - name: Diana Kolusheva
    email: dik431@g.harvard.edu
    affiliation: Harvard University
  - name: Chad Stoughton
    email: ch0793@g.harvard.edu
    affiliation: Harvard University
  - name: Evan Wheeler
    email: evw217@g.harvard.edu
    affiliation: Harvard University
lang: en
format:
  pdf:
    documentclass: scrartcl
    classoption:
    - twocolumn
    margin-left: 25mm
    margin-right: 25mm
    margin-top: 25mm
    margin-bottom: 25mm
    whitespace: medium
    mermaid:
      theme: neutral
    keep-tex: true
bibliography: bibliography.bibtex
# https://stackoverflow.com/a/75043433
template-partials: 
- title.tex
# https://github.com/quarto-dev/quarto-cli/discussions/2786
include-in-header:
  - text: |
      \usepackage[noblocks]{authblk}
      \renewcommand*{\Authsep}{, }
      \renewcommand*{\Authand}{, }
      \renewcommand*{\Authands}{, }
      \renewcommand\Affilfont{\small}
      \usepackage{float}
      \makeatletter
      \let\oldlt\longtable
      \let\endoldlt\endlongtable
      \def\longtable{\@ifnextchar[\longtable@i \longtable@ii}
      \def\longtable@i[#1]{\begin{figure}[H]
      \onecolumn
      \begin{minipage}{0.5\textwidth}
      \oldlt[#1]
      }
      \def\longtable@ii{\begin{figure}[H]
      \onecolumn
      \begin{minipage}{0.5\textwidth}
      \oldlt
      }
      \def\endlongtable{\endoldlt
      \end{minipage}
      \twocolumn
      \end{figure}}
      \makeatother
       \usepackage[font=small,labelfont={bf,small}]{caption}
# https://tex.stackexchange.com/questions/31301/how-to-reduce-the-number-of-hyphenation
include-before-body:
  - text: |
      \pretolerance=5000
      \tolerance=9000
      \emergencystretch=0pt
      \exhyphenpenalty=100
      \righthyphenmin=4
      \lefthyphenmin=5
      \setlength{\belowcaptionskip}{-5pt}
embed-resources: true
notebook-links: false
title-block-banner: true
abstract: |
  The task of forecasting conflict escalation is of great interest to policy makers, executives, and social scientists. In this article, we propose a novel, text-first approach to computational conflict prediction using contemporary natural language processing and machine learning techniques. We outline three methods to extract generalizable conflict signals directly from a corpus of over 2.5 million document embeddings derived from publicly available news sources. The first uses text data enriched by country context features, the second uses text data conditioned only on the country label itself, and the third extracts a signal from the text alone, with no additional country or region-specific features. We demonstrate that signals suggesting impending conflict can be extracted directly from text sources, and we outline potential avenues for further research that we believe may yield models that can provide early warnings to decision makers to facilitate strategic planning, resource allocation, and disaster mitigation.
